Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-03-04 paper/paper.tex
pass on 2.1

@@

\sloppy \nids{} are typically categorized in two
groups~\cite{kumar2007survey}: rule-based (see
Section~\ref{sec:intro}) and anomaly-based \nids. An
\emph{anomaly-based intrusion detector} learn usage behavior from
benign traffic and, based on that, alert uncommon
behavior~\cite{7579764,kumar2007survey,Mitchell:2014:SID:2597757.2542049,cordy-etal-issta19}. More
precisely, an anomaly-based \nids{} flags an attack when the network
traffic manifests different characteristics compared to those of the
benign traffic.

Rule-based \nids\ can miss attacks as rulesets can become outdated
whereas anomaly-based \nids\ can report false alarms as learning
algorithms that generalize observations from bening traffic are
approximate. To sum up, rule-based \nids{} and anomaly-based \nids{}
are complementary---a rule-based \nids{} focuses on known attacks
whereas anomaly-based \nids{} focuses on unknown potential attacks.
This paper focuses on rule-based \nids\ for its tremendous popularity
in industry. Although we focused on the Suricata \nids, the principles
we used are general to any other signature-based \nids~(\eg{},
Snort~\cite{snort}).

>>>>

This section presents background used in the next sections.

@@

\sloppy \nids{} are typically categorized in two
groups~\cite{kumar2007survey}: rule-based, as briefly described on
Section~\ref{sec:intro}, and anomaly-based \nids. An
\emph{anomaly-based intrusion detector} learns usage behavior from
benign traffic and, based on that, alerts uncommon
behavior~\cite{7579764,kumar2007survey,Mitchell:2014:SID:2597757.2542049,cordy-etal-issta19}. More
precisely, an anomaly-based \nids{} flags an attack when the network
traffic manifests different characteristics compared to those of the
benign traffic. Rule-based \nids{} and anomaly-based \nids{} are
complementary. A rule-based \nids{} focuses on known attacks whereas
anomaly-based \nids{} focuses on unknown potential attacks. Rule-based
\nids\ can miss attacks as rulesets can become obsolete whereas
anomaly-based \nids\ can report false alarms as learning algorithms
that generalize observations from bening traffic are approximate.
This paper focuses on rule-based \nids\ for its tremendous popularity
in industry\Fix{cite or tone down}. Although we used Suricata, the
principles we used are general to any other signature-based
\nids~(\eg{}, Snort~\cite{snort}).
